Verifying Demonstrations

### 2019-02-27 paper/verifiability-analysis.tex
Emphasize the malicious protester

As we will show, it follows from \cref{analysis-individual} that the adversary 
cannot drop submitted proof shares and thus cannot decrease the count.
As indicated in the adversary model (\cref{formal-adversary-model}), the 
adversary can submit proof shares as everyone else, so the adversary's only 
option is to increase the count.
We will thus let Alice pose as the adversary in this section, as she naturally 
has an incentive to increase the count, as the organizer and a participant.

>>>>

As we will show, it follows from \cref{analysis-individual} that the adversary 
cannot drop submitted proof shares and thus cannot decrease the count.
As indicated in the adversary model (\cref{formal-adversary-model}), the 
adversary can submit proof shares as everyone else, so the adversary's only 
option is to increase the count.
We will thus let Alice pose as the adversary (malicious protester) in this 
section, as she naturally has an incentive to increase the count, as the 
organizer and a participant.
